---
title: "EMA_DatetoDayofWeek"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This document includes script to add a new variable to the EMA data output. This script adds 'Day of Week' to the table. 

First, read EMA data and select for variables of interest:
```{r}
EMA<- as_tibble(MBMS_EMA_20210622)
EMA <- EMA%>%
  select(`Record ID`,`Event Name`,`Repeat Instance`, `Survey Timestamp`, Distressed, Excited, Upset, Scared, Enthusiastic, Alert, Inspired, Nervous, Determined, Afraid)
```

Then, add 'DayofWeek' variable. THis will classify the weekday from the Survey Timestamp data.
```{r}
EMA <- EMA %>%
  mutate(DayofWeek = weekdays(as.Date(`Survey Timestamp`)), .after= `Survey Timestamp`)

```

Additional variable to classify Weekend and Weekday.
If    DayofWeek = Monday, then Class_DayofWeek = Weekday
      DayofWeek = Tuesday, then Class_DayofWeek = Weekday
      DayofWeek = Wednesday, then Class_DayofWeek = Weekday
      DayofWeek = Thursday, then Class_DayofWeek = Weekday
      DayofWeek = Friday, then Class_DayofWeek = Weekday
      DayofWeek = Saturday, then Class_DayofWeek = Weekend
      DayofWeek = Sunday, then Class_DayofWeek = Weekend
      
  

