---
title: "MBMS_DataAnalysis_Final"
output: html_document
---
Open necessary packages
```{r}
library(tidyverse)
library(tibble)
library(dplyr)
library(data.table)
library(lme4)
library(nlme)
library(ggpubr)
library(rstatix)
library(datarium)

```

Load Dataset: PANAS_Positive_Start
```{r}
library(readxl)
PANAS_Positive_Start <- read_excel("~/Desktop/MBMS Data/PANAS_Positive_Start.xlsx")
View(PANAS_Positive_Start)
```
Load Dataset: PANAS_Negative_Start
```{r}
library(readxl)
PANAS_Negative_Start <- read_excel("~/Desktop/MBMS Data/PANAS_Negative_Start.xlsx")
View(PANAS_Negative_Start)
```
Load Dataset: IOS_Pre
```{r}
library(readxl)
IOS_Pre <- read_excel("~/Desktop/MBMS Data/IOS_Pre.xlsx")
View(IOS_Pre)
```

Remove any missing data from the data set. 
```{r}
PANAS_Positive_Start <- PANAS_Positive_Start%>%
  filter(!is.na("1"),
         !is.na ("2"), 
         !is.na ("3"),
         !is.na ("4"), 
         !is.na ("5"),
         !is.na ("6"), 
         !is.na ("7"))

PANAS_Negative_Start <- PANAS_Negative_Start%>%
  filter(!is.na("1"),
         !is.na ("2"), 
         !is.na ("3"),
         !is.na ("4"), 
         !is.na ("5"),
         !is.na ("6"), 
         !is.na ("7"))

IOS_Pre <- IOS_Pre%>%
  filter(!is.na("1"),
         !is.na ("2"), 
         !is.na ("3"),
         !is.na ("4"), 
         !is.na ("5"),
         !is.na ("6"), 
         !is.na ("7"))
```

To establish significant difference between time points, I will run a Repeated Measures ANOVA for each variable. If this test shows significant difference between sample means at each timepoint, I will continue with further mixed model analysis. 

Set up each data frame for analysis.
```{r}
PANAS_Positive_Start<-PANAS_Positive_Start%>%
  gather(key="time", value="score", "1", "2", "3", "4", "5", "6", "7") %>%
  convert_as_factor(ID)

PANAS_Negative_Start<- PANAS_Negative_Start%>%
 gather(key="time", value="score", "1", "2", "3", "4", "5", "6", "7")%>%
  convert_as_factor(ID)

IOS_Pre <- IOS_Pre%>%
  gather(key="time", value="score", "1", "2", "3", "4", "5", "6", "7") %>%
  convert_as_factor(ID)

```

Y = PANAS_Pos (Scalar)
X = Session (Nominal)

PANAS_POS DESCRIPTIVE STATISTICS
```{r}
##Session Means##
PANAS_Positive_Start %>%
  group_by(time)%>%
  get_summary_stats(type="mean_sd")

```
```{r}
##Individual Means##
PANAS_Positive_Start%>%
  group_by(ID)%>%
  get_summary_stats(type="mean_sd")
```
Create a box plot for individual scores
```{r}
bxp_pos <- ggboxplot(PANAS_Positive_Start, x="time", y="score", add="point") 
bxp_pos
```
Check for Outliers 
```{r}
PANAS_Positive_Start%>%
  group_by(time) %>%
  identify_outliers(score)
```

Check for Normality
```{r}
PANAS_Positive_Start%>%
  ggqqplot("score", facet.by = "time")
```
PANAS_POS REPEATED MEASURES ANOVA
```{r}
anova.PANAS_Pos<- anova_test(data=PANAS_Positive_Start, dv=score, wid = ID, within = time)
get_anova_table(anova.PANAS_Pos)
```
##F(6,60)=1.57, p=0.172


