---
title: "MBMS_DataAnalysis2"
output: html_document
---
Open necessary packages
```{r}
library(tidyr)
library(tibble)
library(dplyr)
library(data.table)
library(lme4)
library(nlme)
```

Read in Baseline, Post, Follow-Up Data
Variables are:
    Ryff's Wellbeing Scale -> Ryff_Total
    Sleep Inventory -> Sleep_Total
    Social Connectedness Scale -> SCS_Total
    Percieved Stress Scale -> PSS_Total
    Mindfulness Inventory -> MI_Total
    Flow State Scale -> Flow_Total
    Meaningfulness of Songwriting -> MofS_Total
    BDI Raw Score Rounded -> BDI_RawScore
    BAI Raw Score Rounded -> BAI_RawScore
  
```{r}
library(readr)
MBMS_BaselinePostFollowup <- read_csv("MBMS-BaselinePostFollowup.csv")
View(MBMS_BaselinePostFollowup)
```

Filter data by event: Baseline, Post, Follow-up
```{r}
MBMS_Baseline <- MBMS_BaselinePostFollowup %>%
  filter(Event=="Baseline")%>%
  select(Ryff_Total, Sleep_Total, SCS_Total, PSS_Total, MI_Total,BDI_RawScore, BAI_RawScore)

MBMS_Post <- MBMS_BaselinePostFollowup %>%
  filter(Event=="Post")%>%
  select(Ryff_Total, Sleep_Total, SCS_Total, PSS_Total, MI_Total,BDI_RawScore, BAI_RawScore)

MBMS_Followup <-MBMS_BaselinePostFollowup %>%
  filter(Event=="Follow-Up")%>%
  select(Ryff_Total, Sleep_Total, SCS_Total, PSS_Total, MI_Total,BDI_RawScore, BAI_RawScore)
```


Run descriptive statistics at each timepoint.
1. Baseline
```{r}
MBMS_Baseline %>%
  sapply (mean,na.rm=TRUE)
MBMS_Baseline %>%
  sapply (sd,na.rm=TRUE) 
MBMS_Baseline %>%
  sapply (range, na.rm=TRUE)
```
2. Post
```{r}
MBMS_Post %>%
  sapply (mean,na.rm=TRUE)
MBMS_Post %>%
  sapply (sd,na.rm=TRUE) 
MBMS_Post %>%
  sapply (range, na.rm=TRUE)
```
3. Follow-Up
```{r}
MBMS_Followup %>%
  sapply (mean,na.rm=TRUE)
MBMS_Followup %>%
  sapply (sd,na.rm=TRUE) 
MBMS_Followup %>%
  sapply (range, na.rm=TRUE)
```

Linear Mixed Model 
