---
title: "MBMS_DataAnalysis_Phase1"
output: html_document
---
Open necessary packages
```{r}
install.packages("lme4")
library(tibble)
library(dplyr)
library(data.table)
library(lme4)
library(nlme)
```

Filter REDCap data for desired IDs. In this round, 12002 is excluded because the child was TD, and 12009 did not complete the study. 
```{r}
PrePostData_Filter <- PrePostData %>%
  filter(Record_ID != "12002" & Record_ID != "12009")
```
I will remove any missing data from the data set. 
```{r}
PrePostData_Filter<- PrePostData_Filter %>%
  filter(!is.na(PANAS_Start_Pos),
         !is.na(PANAS_Start_Neg),
         !is.na(IOS_Pre),
         !is.na(PANAS_End_Pos),
         !is.na(PANAS_End_Neg),
         !is.na(IOS_Post))
```

For the first analysis, I will only be using Pre data points. So, I will filter for only this data.Named _An1 for analysis 1.
```{r}
PreOnlyData_An1 <- PrePostData_Filter %>%
  select(Record_ID, Session, PANAS_Start_Pos, PANAS_Start_Neg, IOS_Pre)

as_tibble(PreOnlyData_An1)
```

Analysis 1 will begin with descriptive statistics of the three variables: PANAS_Start_Pos, PANAS_Start_Neg, IOS_Pre
```{r}
PreOnlyData_An1 %>%
```

Beginning with PANAS_Start_Pos. The data is nested by timepoint 1,2,3,4,5,6,7. First, plot PANAS_Start_Pos by timepoint. 
```{r}
PANAS_Pos_lm=lm(PANAS_Start_Pos ~ Session, data=PreOnlyData_An1)
summary(PANAS_Pos_lm)
```
## Output shows the following
## Residual standard error =8.898, df(80)
## R2= 0.0024, Adjusted R2= -0.010
## F(1,80)=0.1954, p=0.6597, P>.05
```{r}
PANAS_Pos_mixed =lmer(PANAS_Start_Pos ~ Session + (1|Record_ID), data=PreOnlyData_An1)

summary(PANAS_Pos_mixed)

confint(PANAS_Pos_mixed)
```



```{r}
