---
title: "MBMS_PrePostFollowup_DataAnalysis_Final"
output: html_document
---
Open necessary packages
```{r}
library(tidyverse)
library(tibble)
library(dplyr)
library(data.table)
library(lme4)
library(nlme)
library(ggpubr)
library(rstatix)
library(datarium)
library(readr)
```

Load Dataset
```{r}
BaselinePostFollowup <- read_csv("MBMSMAINDatabase-BaselinePostFollowup_DATA_LABELS_2021-07-22_1124.csv")
```
Remove any missing data from the data set. 
```{r}
BaselinePostFollowup <- BaselinePostFollowup%>%
  filter(ID != "12002" & ID != "12009") %>%
  filter(!is.na("time"),!is.na("ryff"),!is.na("sleep"),!is.na("scs"),!is.na("pss"),!is.na("mi"),!is.na("fss"),!is.na("mofs"),!is.na("bdi"),!is.na("bai"))
```

To establish significant difference between time points, I will run a Repeated Measures ANOVA for each variable. If this test shows significant difference between sample means at each timepoint.

Separate each variable and set up data frame for analysis. 
```{r}
ryff <- BaselinePostFollowup[,c("ID", "time", "ryff")]
ryff<- ryff%>%
  convert_as_factor(ID)
```

```{r}
sleep <- BaselinePostFollowup[,c("ID", "time", "sleep")]
sleep<- sleep%>%
  convert_as_factor(ID)
```

```{r}
scs <- BaselinePostFollowup[,c("ID", "time", "scs")]
scs<- scs%>%
  convert_as_factor(ID)
```

```{r}
pss <- BaselinePostFollowup[,c("ID", "time", "pss")]
pss<- pss%>%
  convert_as_factor(ID)
```

```{r}
mi <- BaselinePostFollowup[,c("ID", "time", "mi")]
mi<- mi%>%
  convert_as_factor(ID)
```

```{r}
fss <- BaselinePostFollowup[,c("ID", "time", "fss")]
fss<- fss%>%
  convert_as_factor(ID)
```

```{r}
mofs <- BaselinePostFollowup[,c("ID", "time", "mofs")]
mofs<- mofs%>%
  convert_as_factor(ID)
```

```{r}
bdi <- BaselinePostFollowup[,c("ID", "time", "bdi")]
bdi<- bdi%>%
  convert_as_factor(ID)
```

```{r}
bai <- BaselinePostFollowup[,c("ID", "time", "bai")]
bai<- bai%>%
  convert_as_factor(ID)
```

DESCRIPTIVE STATISTICS 
```{r}
##Session Means##
ryff %>%
  group_by(time)%>%
  get_summary_stats(type="mean_sd")
sleep %>%
  group_by(time)%>%
  get_summary_stats(type="mean_sd")
scs %>%
  group_by(time)%>%
  get_summary_stats(type="mean_sd")
pss %>%
  group_by(time)%>%
  get_summary_stats(type="mean_sd")
mi %>%
  group_by(time)%>%
  get_summary_stats(type="mean_sd")
fss %>%
  group_by(time)%>%
  get_summary_stats(type="mean_sd")
mofs %>%
  group_by(time)%>%
  get_summary_stats(type="mean_sd")
bdi %>%
  group_by(time)%>%
  get_summary_stats(type="mean_sd")
bai%>%
  group_by(time)%>%
  get_summary_stats(type="mean_sd")

```

Create box plot for each measure
```{r}
bxp_ryff <- ggboxplot(ryff, x="time", y="ryff", add="point") 
bxp_ryff
bxp_sleep <- ggboxplot(sleep, x="time", y="sleep", add="point") 
bxp_sleep
bxp_scs <- ggboxplot(scs, x="time", y="scs", add="point") 
bxp_scs
bxp_pss <- ggboxplot(pss, x="time", y="pss", add="point") 
bxp_pss
bxp_mi <- ggboxplot(mi, x="time", y="mi", add="point") 
bxp_mi
bxp_bdi <- ggboxplot(bdi, x="time", y="bdi", add="point") 
bxp_bdi
bxp_bai <- ggboxplot(bai, x="time", y="bai", add="point") 
bxp_bai
bxp_fss <- ggboxplot(fss, x="time", y="fss", add="point") 
bxp_fss
bxp_mofs <- ggboxplot(mofs, x="time", y="mofs", add="point") 
bxp_mofs
```

Create QQ plot for each measure
```{r}
  ggqqplot(ryff, "ryff", facet.by = "time")
  ggqqplot(sleep, "sleep", facet.by = "time")
  ggqqplot(scs, "scs", facet.by = "time")
  ggqqplot(pss, "pss", facet.by = "time")
  ggqqplot(mi, "mi", facet.by = "time")
  ggqqplot(bdi,"bdi", facet.by = "time")
  ggqqplot(bai,"bai", facet.by = "time")
  ggqqplot(fss,"fss", facet.by = "time")
  ggqqplot(mofs,"mofs", facet.by = "time")

```{r}
```
Check for Outliers 
```{r}
ryff%>%
  group_by(time) %>%
  identify_outliers(ryff)
sleep%>%
  group_by(time) %>%
  identify_outliers(sleep) 
scs%>%
  group_by(time) %>%
  identify_outliers(scs) 
pss%>%
  group_by(time) %>%
  identify_outliers(pss) 
mi%>%
  group_by(time) %>%
  identify_outliers(mi)
bdi%>%
  group_by(time) %>%  
  identify_outliers(bdi)
bai%>%
  group_by(time) %>%
  identify_outliers(bai)
fss%>%
  group_by(time) %>%
  identify_outliers(fss)
mofs%>%
  group_by(time) %>%
  identify_outliers(mofs)
```

REPEATED MEASURES ANOVAs
```{r}
anova.ryff<- anova_test(data=ryff, dv=ryff, wid = ID, within = time)
get_anova_table(anova.ryff)
```
```{r}
anova.sleep<- anova_test(data=sleep, dv=sleep, wid = ID, within = time)
get_anova_table(anova.sleep)
```
```{r}
anova.scs<- anova_test(data=scs, dv=scs, wid = ID, within = time)
get_anova_table(anova.scs)
```
```{r}
anova.pss<- anova_test(data=pss, dv=pss, wid = ID, within = time)
get_anova_table(anova.pss)
```
```{r}
anova.mi<- anova_test(data=mi, dv=mi, wid = ID, within = time)
get_anova_table(anova.mi)
```
```{r}
anova.bdi<- anova_test(data=bdi, dv=bdi, wid = ID, within = time)
get_anova_table(anova.bdi)
```

```{r}
anova.bai<- anova_test(data=bai, dv=bai, wid = ID, within = time)
get_anova_table(anova.bai)
```
Account for extreme outliers:
BDI, Time=3, ID=12010
BAI, Time=3, ID = 12003
```{r}
bdi_Filter <- bdi[-c(24),]
anova.bdi_filter <-anova_test(data=bdi_Filter, dv=bdi, wid = ID, within = time)
get_anova_table(anova.bdi_filter)
```

```{r}
bai_filter <- bai[-c(6),]
anova.bai_filter <-anova_test(data=bai_filter, dv=bai, wid = ID, within = time)
get_anova_table(anova.bai_filter)
```


