---
title: "PANASPreNeg_MBMS_Final"
output: html_document
---
Open necessary packages
```{r}
library(tidyverse)
library(tibble)
library(dplyr)
library(data.table)
library(lme4)
library(nlme)
library(ggpubr)
library(rstatix)
library(datarium)
```
Load Dataset: PANAS_Negative_Start
```{r}
library(readxl)
PANAS_Negative_Start <- read_excel("~/Desktop/MBMS Data Analysis/PANAS_Negative_Start.xlsx")
View(PANAS_Negative_Start)
```

```{r}
PANAS_Negative_Start <- PANAS_Negative_Start%>%
  filter(ID != "12002" & ID != "12009") %>%
  filter(!is.na("1"),
         !is.na ("2"), 
         !is.na ("3"),
         !is.na ("4"), 
         !is.na ("5"),
         !is.na ("6"), 
         !is.na ("7"))
```

The model: Mixed model with variables ID, Time, and Score. Time is fixed. 

Set up each data frame for analysis.
```{r}
PANAS_Negative_Start<-PANAS_Negative_Start%>%
  gather(key="time", value="score", "1", "2", "3", "4", "5", "6", "7") %>%
  convert_as_factor(ID) 
  
as.numeric(unlist("score"))
score<- as.numeric("score")
```

Check for Normality
```{r}
PANAS_Negative_Start%>%
  ggqqplot("score", facet.by = "time")
```
Load in data set: PANAS Negative- Mean Centered
```{r}
library(readxl)
PANAS_Neg_Scale <- read_excel("PANAS_Neg_scale.xlsx", 
    sheet = "Mean-Centered", col_types = c("text", 
        "text", "numeric"))
```

Check for Normality
```{r}
PANAS_Neg_Scale%>%
  ggqqplot("score", facet.by = "time")
```
I'll plot the centered data before running an analysis model. 
```{r}
lineplot <- ggplot(data=PANAS_Neg_Scale, aes(y=score, x=time, color=ID, group=ID)) + 
  geom_point() + geom_line() +
  ggtitle("Negative PANAS Scores across Sessions, by individual ") + 
  theme(legend.position = "none") + scale_x_discrete(breaks = c(1, 2, 3, 4, 5, 6, 7))
lineplot

```

Fit a mixed model for PANAS Negative data frame.
```{r}
model2<- lmer(score ~ time + (1|ID), data=PANAS_Neg_Scale)
summary(model2)
anova(model2)

```
# Estimate of the variance explained by the random effect (ID)# 
      = 13.944 (3.734)
      resid= 6.842 (low)
      
# Estimate of the fixed effects of time#
      intercept = 3.319 
      time2 = -2.250
      time3 = -3.583
      time4 = -3.583
      time5 = -3.417
      time6 = -4.833
      time7 = -5.385
      
```{r}
ci2 <- confint(model2, method="boot", nsim=10)
ci2 <- tibble::rownames_to_column(data.frame(ci2), "Term") 
colnames(ci2)<- c("Term", "CI 2.5%", "CI 97.5%")
knitr::kable(ci[3:9,])
```
# Estimate of the fixed effects of time#
      intercept = 3.319 **
      time2 = -2.250
      time3 = -3.583
      time4 = -3.583 **
      time5 = -3.417
      time6 = -4.833 **
      time7 = -5.385 **
      



```{r}
ggplot(data=PANAS_Neg_Scale, 
       aes(y=score, x=time, color=ID, group=ID)) + 
  geom_point() + geom_line() +
  scale_color_manual(values = c("dodgerblue4","dodgerblue2","steelblue3", "steelblue1","lightsteelblue3","lightsteelblue1","lightskyblue4","lightskyblue3","lightskyblue1","paleturquoise3","paleturquoise1","royalblue1"))+
  ggtitle("Negative PANAS Scores across Sessions") + 
  theme(legend.position = "none") + 
  scale_x_discrete(breaks = c(1, 2, 3, 4, 5, 6, 7))+
  geom_abline(intercept = fixef(model2)[1], #Regression Line (RL).
              slope=fixef(model2)[2], col="red") +                
  geom_abline(intercept = ci2$`CI 97.5%`[5], 
              slope=ci2$`CI 97.5%`[6], col="black") + #Upper Bound of RL
  geom_abline(intercept = ci2$`CI 2.5%`[5], 
              slope=ci2$`CI 2.5%`[6], col="black") + #Lower Bound of RL
  geom_text(aes(2, -1.25, label="X"), col="red", size=10)
```

